Delayed effects of climate on vital rates lead to demographic divergence in Amazonian forest fragments

### 2021-08-24 review/Response to reviews.Rmd

> Fig 3 -- I mentioned this earlier, but I wasn't really clear on how to interpret effect size.
> I see the explanation in L 539 in the legend, but I don't really know what that means.
> Since this is such an important result of the paper, it would help the reader if they were walked through this idea.
> What is a negative vs. positive effect size in relation to plant size (does this compare to the median size)?
> I am likely missing something here.
> (I think the challenge for me is that I kept wanting the figures to fit into a more standard demographic paper -- like the probability of survival based on size, but then I realized something different was being shown here.)

These plots were the evaluated smooths on the link scale.
We agree that they were difficult to interpret in that form, so we have added the model intercept and back-transformed them to be on their respective response scales (e.g. probability for flowering and survival).
This is equivalent to the marginal effect of log(size_t)---that is, without considering the additive effect of lagged SPEI or the random intercepts for different plots and for plants that had not flowered in the previous year (the reference level for the `flwr_prev` factor we included as a parametric covariate).
We have not clarified that in the figure caption.

> Figs 4 -- 6 -- Where the isocline circles are large, does that mean it's a very large time span?
> I was a bit confused when describing the results of Fig 4b (L296-297), for example, the lag is described as the preceding 13 months in the 1 ha fragment, rather than 0 -- 13 months (although now I see maybe the word preceding was meant to indicate this whole range).
> A little bit more explanation in the legends would help these figures be more intuitive.

We've revised the figure captions to clarify: *"Outlines show combinations of SPEI and lag time that have a significant effect on survival, defined as areas where the 95% confidence interval around the response does not overlap the intercept."*

@@

...see also our response to \@ref(R1-3)

##  {#R3-10}

> Figure 4 and 5 -- very nice way to display the confidence limit.
> I did have to spend a while looking at them and doing a bit of head scratching to figure out which side the significant values were on, especially for the ones that are along the middle where the difference in color is not large.
> I wonder if a diverging color scheme with values close to the mean set to white would make this easier to see?
> Or if you could add some hatching or change the alpha transparency on one side to highlight those regions more clearly.

In the updated version of figure 4 (see response to \@ref(R3-5)), a smaller area of the plot is significantly different from the intercept, and heatmap area far from observed data is grayed out.
We believe these two things make it easier to see the outlines around significant values, but we are open to trying other modifications of the plot if the reviewers think it is still difficult to interpret in this way.

### 2021-08-24 doc/paper.Rmd
edits to figure captions (#83, closes #95)

```{r}
s_spei_cap <- "Smooth effect of lagged SPEI on *H. acuminata* survival in (a) continuous forest, (b) 1-ha fragments, (c) and the difference between the two. Outlines show regions where the effect of SPEI is significant, defined as those where the 95% confidence interval around the response does not overlap the intercept. The bar on the bottom of each panel indicates the wet seasons (black, November–May) and dry seasons (white, June–October). Surface is modeled as a crossbasis function with cubic regression splines for each marginal basis. Model intercepts were added to fitted values of the crossbasis function and back-transformed to the response scale."

@@

```{r}
g_spei_cap <- "Smooth effect of lagged SPEI on *H. acuminata* growth in (a) continuous forest, (b) 1-ha fragments, (c) and the difference between the two. Outlines show regions where the effect of SPEI is significant, defined as those where the 95% confidence interval around the response does not overlap the intercept. The bar on the bottom of each panel indicates the wet seasons (black, November–May) and dry seasons (white, June–October)."
```

@@

```{r}
f_spei_cap <- "Smooth effect of lagged SPEI on *H. acuminata* flowering probability in (a) continuous forest, (b) 1-ha fragments, (c) and the difference between the two. Outlines show regions where the effect of SPEI is significant, defined as those where the 95% confidence interval around the response does not overlap the intercept. The bar on the bottom of each panel indicates the wet seasons (black, November–May) and dry seasons (white, June–October). Surface is modeled as a crossbasis function with cubic regression splines for each marginal basis. Model intercepts were added to fitted values of the crossbasis function and back-transformed to the response scale."
```

>>>>

```{r}
s_spei_cap <- "Marginal effect of lagged SPEI on *H. acuminata* survival in (a) continuous forest, (b) 1-ha fragments, (c) and the difference between the two. Outlines show combinations of SPEI and lag time that have a significant effect on survival, defined as areas where the 95% confidence interval around the response does not overlap the intercept. The bar on the bottom of each panel indicates wet seasons (black, November–May) and dry seasons (white, June–October). For a and b, the model intercepts were added to the evaluated crossbasis smooths and values were back-transformed to the response scale (i.e. probabilities). Areas of the fitted smooth far from observed values (i.e. combinations of lag time and SPEI) are shown in grey."

@@

```{r}
g_spei_cap <- "Marginal effect of lagged SPEI on *H. acuminata* size in (a) continuous forest, (b) 1-ha fragments, (c) and the difference between the two. Outlines show combinations of SPEI and lag time that have a significant effect on plant size, defined as areas where the 95% confidence interval around the response does not overlap the intercept.  The bar on the bottom of each panel indicates wet seasons (black, November–May) and dry seasons (white, June–October). For a and b, the model intercepts were added to the evaluated crossbasis smooths. Areas of the fitted smooth far from observed values (i.e. combinations of lag time and SPEI) are shown in grey."
```

@@

```{r}
f_spei_cap <- "Marginal effect of lagged SPEI on *H. acuminata* flowering probability in (a) continuous forest, (b) 1-ha fragments, (c) and the difference between the two. Outlines show combinations of SPEI and lag time that have a significant effect on probability of flowering, defined as areas where the 95% confidence interval around the response does not overlap the intercept.  The bar on the bottom of each panel indicates wet seasons (black, November–May) and dry seasons (white, June–October). For a and b, the model intercepts were added to the evaluated crossbasis smooths and values were back-transformed to the response scale (i.e. probabilities). Areas of the fitted smooth far from observed values (i.e. combinations of lag time and SPEI) are shown in grey."
```
